The \dealii{} Library, Version 8.5

### 2017-03-21 8.5/paper.tex
Minor edits.

\texttt{CellDataStorage} can work with arbitrary kinds of data defined to live on a cell
as long as the corresponding data type implements a default constructor.
Additionally, when a user's custom data type is derived from \texttt{TransferableQuadraturePointData}
and thereby implements certain interface,
then the \texttt{parallel::distributed::ContinuousQuadratureDataTransfer} class
can transfer this data during $h$-adaptive refinement from parent cell to children
(interpreting the data on quadrature points as discrete representations of an
underlying continuous field),
as well as from one processor to another during repartitioning.

@@

\marginpar{Add your funding here as appropriate}
D.~Arndt was supported by the German Research Foundation (DFG) under the
project ``High-order discontinuous Galerkin for the exa-scale'' (ExaDG) within the
priority program ``Software for Exascale Computing'' (SPPEXA).

>>>>

\texttt{CellDataStorage} can work with arbitrary kinds of data defined to live on a cell
as long as the corresponding data type implements a default constructor.
Additionally, when a user's custom data type is derived from \texttt{TransferableQuadraturePointData}
and thereby implements certain interfaces,
then the \texttt{parallel::distributed::ContinuousQuadratureDataTransfer} class
can transfer this data during $h$-adaptive refinement from parent cell to children
(interpreting the data on quadrature points as discrete representations of an
underlying continuous field),
as well as from one processor to another during repartitioning.

@@

D.~Arndt was supported by the German Research Foundation (DFG) under the
project ``High-order discontinuous Galerkin for the exa-scale'' (ExaDG) within the
priority program ``Software for Exascale Computing'' (SPPEXA).
